---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# bugger

<!-- badges: start -->
<!-- badges: end -->

The goal of bugger is to help explain some of the more frequent, and frequently
miunderstood, error messages in R.

If you googled for "Error in {`some_function`}: object of type 'closure'
is not subsettable" in your first week learning _R_, hopefully you'll
understand that _R_'s error messages are somewhat opaque.

## Installation

You can install the released version of bugger from [github](https://github.com/russHyde/bugger.git) with:

``` r
# library(devtools)
devtools::install_github("russHyde/bugger")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bugger)
## basic example code
```

```
# not ran
bugger("Error in mean[1]: object of type 'closure' is not subsettable")
```

This should open up a man page that explains the error in a bit more detail.
